### 2020-08-10 LaTeX/sections/paper.tex
Added SGX for closing

\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly. ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge. ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate. These proofs could be generated (i) for free or (ii) we could charge market participants fo them.

\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (also known as the challenge period). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. Also, assertions are publicly available and privacy of data is not protected. However, this does not affect our application as the new state only reflects the updated balances of traders and no secret is involved.

@@

>>>>

\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly. ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge. ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate. These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.

\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a. "the challenge period'). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. Also, assertions are publicly available and privacy of data is not protected. However, this does not affect our application as the new state only reflects the updated balances of traders and no secret is involved.

@@

%= = = = = =  = =  =  SGX=  = = = = = = = = =%
\item \textbf{{Using Intel SGX technology.}} Another solution pattern to close the market is to use SGX technology; a trusted execution environment~\cite{anati2013innovative}. In this method, the enclave can execute the \texttt{CloseMarket()} function offline and publishes an attestation Quote to the CallMarket contract. The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
